Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-22 paper-2023-acsos-pulverization.tex
Fig on approach: minor fixes + larger text

\begin{figure}
\includegraphics[width=\columnwidth]{figures/pulverization-framework-overview.drawio.pdf}
\caption{
    The approach provides two \acp{dsl}
    and a runtime for specifying and executing deployment plans.
    %
    Each deployment unit will be delivered to the target site
    and properly configured to interact with other deployment units
    as the application at hand requires (see  \Cref{sec:evaluation} for examples).
}
\label{fig:approach}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{figures/pulverization-framework-overview.drawio.pdf}
\caption{
    The approach provides two \acp{dsl}
    and a runtime for specifying and executing deployment plans.
    %
    Each deployment unit will be delivered to the target site
    and properly configured to interact with other deployment units according to the protocal 
    that the application at hand requires (see  \Cref{sec:evaluation} for examples).
}
\label{fig:approach}
\end{figure}
